Quality assurance of digital twins: An experience report in the automotive industry

### 2023-07-04 manuscripts/paper-1/Without_Names.tex
Reworked

@@

    \section{Introduction}\label{section:introduction}
    The notion of the digital twin, which has gained popularity in recent years, is often subject to vague and ambiguous envisions~\cite{Review1}.
    The mispresenting of this notion began with the physical twin of the Apollo 13 spacecraft. 
    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations. 
    Even though the digital aspect was expected to be present, there wasn't~\cite{GrievesMichaelApolloMyth}.
    Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
    which was used simultaneously before and during the operation, and can be argued to be similar. 
    The board was a twin of the operation, and it included models of battalions and ships that reflected the actual 
    locations of the corresponding formations. Furthermore, synchronization was 
    implemented to give directives from the real system to control the operation 
    flow and to update the physical twin state~\cite{AMRC}.
    In contrast, a digital twin is virtual information of a possible or constructed real system, which can 
    be synchronized with a selected frequency and fidelity~\cite{Review1,Review2,digitaltwinconsortium2022}.

@@

    \section{Method}
    The form of FELICE's digital twin was the digital twin instance\cite{GrievesVickers2017}, 
    which implies that the real system was already constructed. It is important to note that, for the sake of convenience, the authors used the term "Digital Twin" in the subsequent chapters instead of  "digital twin instance" in the subsequent chapters.

    Moreover, since the digital twin was still in the design phase, 
    the methodology of assessing its quality consists of several key steps,
    including a set of artifacts, manual reviews of these artifacts, 
    mapping quality attributes to the identified findings, an evaluation of the artifact quality, and ultimately, 
    an evaluation of the digital twin's overall quality.
    \subsection{Artifacts}\label{section:Artifacts}
    The current stage of review encompassed five key artifacts,
    including process videos displaying the current assembly procedure without an adaptive workstation and cobot,
    a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements 
    specification summarizing functional and non-functional requirements for the digital twin, a general and an operational 
    conceptual model elucidating the high-level structure of the assembly procedure, 
    and a discrete event simulation module that implements the structures prescribed by the conceptual models.

@@

    \textbf{Correctness} is a  derived word from the adjective \textit{correct}, which means that the entity is error-free regarding fact or truth. 
    In the context of the digital twins, the fact or truth is the real system hence, \textit{correctness} is a grade of quality, 
    that indicates an error between the real system and a digital twin system (Figure~\ref{fig:CorrectnessAndCompleteness}).
    Meanwhile, the quality of being \textit{correct} is described by the term accuracy~\cite{OxfordDictionary}.

@@

    Two examples(Finding 12, Finding 18) are given to the reader to illustrate 

@@

    \newpage
    \bibliography{main}
    \bibliographystyle{splncs04}

>>>>

    \author{Alican Tüzün
    \and
    Georg Hackenberg
    }
    \institute{School of Engineering\\
    University of Applied Sciences Upper Austria\\
    4600 Wels, Upper Austria, Austria\\
    \email{alican.tuzuen@fh-wels.at}
    \email{georg.hackenberg@fh-wels.at}
    }

@@

    \section{Introduction}\label{section:introduction}
    The notion of the digital twin, which has gained popularity in recent years, is often subject to vague and ambiguous envisions~\cite{Review1}.
    The mispresenting of this notion began with the physical twin of the Apollo 13 spacecraft. 
    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations. 
    Even though the digital aspect was expected to be present, there wasn't~\cite{GrievesMichaelApolloMyth}.
    Another physical twin is the historic D-Day map (also known as the Big Board) in Southwick House England, 
    which was used simultaneously before and during the operation, and can be argued to be similar. 
    The board was a twin of the operation, and it included models of battalions and ships that reflected the actual 
    locations of the corresponding formations. Furthermore, synchronization was 
    implemented to give directives from the real system to control the operation 
    flow and to update the physical twin state~\cite{AMRC}.
    In contrast, a digital twin is virtual information of a possible or constructed real system, which can 
    be synchronized with a selected frequency and fidelity~\cite{Review1,Review2,digitaltwinconsortium2022}.

@@

    \section{Method}
    The form of FELICE's digital twin was the digital twin instance\cite{GrievesVickers2017}, 
    which implies that the real system was already constructed. 
    It is important to note that, for the sake of convenience, 
    the authors utilized the term `Digital Twin' in the subsequent chapters instead of `digital twin instance'.

    Moreover, since the digital twin was still in the design phase, 
    the methodology of assessing its quality consists of several key steps,
    including identification of the artifacts, manual reviews of these artifacts, 
    mapping quality attributes to the identified findings, an evaluation of the artifact quality, and ultimately, 
    an evaluation of the digital twin's overall quality.
    \subsection{Artifacts}\label{section:Artifacts}
    The current stage of review encompassed five key artifacts,
    including process videos displaying the current assembly procedure without an adaptive workstation and cobot,
    a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements 
    specification summarizing functional and non-functional requirements for the digital twin, a general and an operational 
    conceptual model elucidating the high-level structure of the assembly procedure, 
    and a discrete event simulation module that implements the structures prescribed by the conceptual models.

@@

    \textbf{Correctness} is a  derived word from the adjective \textit{correct}, which means that the entity is error-free regarding fact or truth. 
    In the context of the digital twins, the fact or truth is the real system hence, \textit{correctness} is a grade of quality, 
    that indicates an error between the real system and a digital twin system (Figure~\ref{fig:CorrectnessAndCompleteness}).
    Meanwhile, the quality of being \textit{correct} is measured by the metric accuracy~\cite{OxfordDictionary}.

@@

    Two examples (Finding 12, Finding 18) are given to the reader to illustrate 

@@

    \section*{Acknowledgement}
    The authors express their sincere gratitude to the FELICE project under GAID (101017151) and its dedicated members 
    for their invaluable feedback and strong patience throughout the evaluation of the digital twin's quality.
    \bibliography{main}
    \bibliographystyle{splncs04}
